\documentclass[margin,line]{res}

\makeatletter
\renewenvironment{thebibliography}[1]
     {%\section*{\refname}% <--- outcommented
      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
      \list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newenvironment{list3}{
  \begin{list}{
      \setlength{\leftmargin}{0.25in}}}{\end{list}}

\begin{document}

\name{Efstathios Ch. Kamperis \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Doiranis 23 Street           & {\it Voice:}   (+30) 2310 848593 \\
Thessaloniki, 54638 Greece   & {\it Mobile:}  (+30) 6976 761308 \\
                             & {\it E-mail:}  ekamperi@gmail.com\\
\end{tabular}

%_______________________________________________________________________________
\section{\sc Education}
{\bf Aristotle University}, Thessaloniki, Greece\\
{\em Faculty of Sciences, School of Physics}\\
Undergraduate student \hfill {\bf Sep, 2008 - }\\

{\bf Aristotle University}, Thessaloniki, Greece\\
{\em Department of Medicine}\\
Graduate Student (Grade: 7.71/10) \hfill {\bf Sep, 2000 - Jun 2007}\\

{\bf High School}, Thessaloniki, Greece\\
Graduate Student (Grade: 19.67/20) \hfill {\bf Sep, 2000}\\

%_______________________________________________________________________________
\section{\sc Working experience}
{\bf Theagenion Anti-Cancer Hospital}, Thessaloniki, Greece\\
{\em Resident Physician - Radiotherapy Oncology}
\hfill {\bf 2010 - }\\

{\bf Google Summer of Code 2012}\\
{\em Funded by Google Inc. to work on CERN's Geant4 simulation framework.}
\hfill {\bf May, 2012 - Aug, 2012}\\

{\bf Google Summer of Code 2011}\\
{\em Funded by Google Inc. to work on NetBSD's pkgsrc packaging system.}
\hfill {\bf May, 2011 - Aug, 2011}\\

{\bf Google Summer of Code 2010}\\
{\em Funded by Google Inc. to audit and extend NetBSD's Operating\\ System math library.}
\hfill {\bf May, 2010 - Aug, 2010}\\

{\bf Google Summer of Code 2009}\\
{\em Funded by Google Inc. to audit DragonFlyBSD Operating System\\ against the latest POSIX and C99 standards.}
\hfill {\bf May, 2009 - Aug, 2009}\\

{\bf Military serice}\\
{\em Served my mandatory military service as an enlisted doctor\\in 490 Communications Battalion of NDC-GR.}
\hfill {\bf Jan, 2008 - Nov, 2008}\\

{\bf Gennimatas Hospital}, Thessaloniki, Greece\\
{\em Intern in the Gastric Motility \& Manometry Lab} \hfill {\bf Sep, 2000 - Nov, 2007}\\
Working in 24-h oesophageal pH-metry, oesophageal manometry\\
and anorectal manometry.

%_______________________________________________________________________________
\section{\sc Languages}
\begin{list2}
\item English (FCE 1997, CAE 2003, CPE 2004, Michigan Proficiency 2004)
\item Italian (Diploma di lingua Italiana 1995)
\item Greek (Mother language)
\end{list2}

%_______________________________________________________________________________
\section{\sc Computer Skills}
\small (Sorted descendingly from proficient to intermediate level of knowledge)
\normalsize
\begin{list2}
\item Operating Systems: Linux, BSD, Windows, Solaris
\item Programming languages: C, C++, Java, POSIX shell scripting, Ruby, DTrace
\item Programming Toolkits: Qt, Gtk
\item Applications: \LaTeX, MS Office
\item Statistical Packages: SPSS, R
\item Computer Algebra Systems: Mathematica, Matlab, Maxima
\item Version Control Systems: Git, Hg (mercurial), CVS
\item Hardware: Embedded development with AVR 8bit microcontrollers (LEDs, LCDs,
stepper mottors, A/D converters, temperature sensors)
\item {\bf DragonFly BSD developer} with commit access\\\small http://www.dragonflybsd.org/team/,
https://www.ohloh.net/accounts/ekamperi\normalsize
\begin{list3}
\item Standards conformance, regression testing, userland maintenance,
occasional kernel level hacking, documentation
\item During {\bf Google Summer of Code 2009} ported POSIX message queues from
NetBSD, complex arithmetic functions from FreeBSD, developed a test case
framework, wrote more than 200 test cases and a conformance tracking site in PHP.
\end{list3}
\item {\bf NetBSD developer}
\begin{list3}
\item Standards conformance, regression testing, quality assurance
\item During {\bf Google Summer of Code 2010} wrote more than 250 test cases for
NetBSD's math library and ported fenv.h interface from FreeBSD for x86, amd64 and
spar64 architectures.
\end{list3}
\item {\bf Package maintainer} in pkgsrc-wip project with CVS write access \\http://pkgsrc-wip.sourceforge.net/
\item Various contributions to free/open source projects (GNOME Internationalization project for Greek language,
NetBSD wiki documentation project)
\end{list2}

%_______________________________________________________________________________
\section{\sc Honors and Awards}
First prize at Hellenic Mathematic Society (HMS) Competition, Thessaloniki, 2000\\
First prize at Hellenic Mathematic Society (HMS) Competition, Thessaloniki, 2001

%_______________________________________________________________________________
\section{\sc Certificates, recommendations, source code samples}
Readily available upon request\\\\\\

%_______________________________________________________________________________
\section{\sc Publications}
\renewcommand\refname{}
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{mycv}
\end{resume}

\end{document}
